CF Registry Analysis

### 2023-12-06 Christine Chan/CF Registry/cf_registry_analysis.qmd
Update cf_registry_analysis.qmd

```{r}
#| include: false
library(Hmisc)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(parallel)
```

>>>>

```{r}
#| include: false
library(Hmisc)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(parallel)
switch(Sys.info()[["sysname"]],
  Windows = {
    home_dir <- "OneDrive - The University of Colorado Denver"
  },
  Darwin = {
    home_dir <- "~/"
  }
)
knitr::opts_knit$set(root.dir = home_dir)
```
